%------------------------
% Resume
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Shihui Zhu}} & Email: \href{mailto:}{sz3029@cumc.columbia.edu}\\
  \href{https://xprilion.com}{Linkedin: https://www.linkedin.com/in/shihui-zhu-319266173/} & Mobile:~~~+1(858)-736-5630 \\
  \href{https://github.com/sz3029}{Github: ~~github.com/sz3029} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
% undergrad
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{San Diego, CA}
      {Bachelor of Science - Mathematics-CS and Bioengineering:Bioinformatics;  GPA: 3.7}{Sep. 2017 - June 2021}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Data Structures, Algorithms, Machine Learning, Databases, Bioinformatics, NGS}}}
  % grad
    \resumeSubheading
      {Columbia University}{New York, NY}
      {Master of Science - Biostatistics (Theory and Method Track);  GPA: 3.9}{Sep. 2021 - Present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Statistics Inference, Machine Learning, Deep Learning, Data Mining, Databases, RCT, Longitudinal and Survival Analysis}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~~~Python, R, SAS, SQL, C++, Bash, JAVA}
	\resumeSubItem{Frameworks}{~~~~~~Scikit, Pytorch, TensorFlow, Pandas, Caret, Tidyverse, Flask}
	\resumeSubItem{Tools and IDEs}{~GIT, MySQL, Pycharm, DataGrip}
	\resumeSubItem{Platforms}{~~~~~~~~~Linux, Web, Windows, Raspberry, AWS, Azure}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Research Assistant at Columbia University Medical Center}{New York, NY}
    {Clinical Research (ML) (On Campus, Part-time)}{Oct. 2021 - Present}
    \resumeItemListStart
        \resumeItem{Data Collection and EDA}
          {Data Cleaning, Feature Selection and AB testing for 1M rows of Clinical Data (30-day mortality) from Anesthesiology Department. Bootstrapping to accommodate Data Imbalanceness.}
          \resumeItem{Modeling and Model Evaluation}
          {Data Normalization and Standardization. Evaluation via CV for traditionally used subset selection and Tree Models, ML models Random Forest, XGBoosting, Logistic Regression, and DNN model.}
          \resumeItem{Model Interpretation}{Interpreted model prediction via SHAP values. Interpreted how much each feature contributed differently among different patients.}
      \resumeItemListEnd
\vspace{-5pt}
    \resumeSubheading
		{Yrobot Inc.}{Remote}
		{Data Analyst and Machine Learning (Internship)}{May 2022 -  Sep. 2022}
		\resumeItemListStart
        \resumeItem{Libraries for walking data analysis}
          {Created python libraries that formulate the raw IMU sensor data, and design plots for patients' walking data analysis via plotly}
        \resumeItem{DNN-based model adaptation for 3D Human Motion Estimation}
          {Adapted the model for the company's experimental data.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{ML - Improving Automated CLL/ALL Diagnosis via Machine Learning and CNN models on Flow Cytometry Dataset}{High-dimensional Flow Cytometry Data Classification for Leukemia patients via the UMAP and CNN models. Tech: Python, Scikit, matlibplot (June '21).
    Project Website: \url{https://sites.google.com/ucsd.edu/group232021leukemiadiagnosis}}
\vspace{2pt}
\resumeSubItem{ML - Training and Comparing Machine Learning Models for HCV diagnosis}{Use linear regression, logistic regression, GLM, discriminant analysis and tree models to improve the traditional HCV diagnosis. (Oct. '21). Tech: R. Project Website: \url{https://github.com/MefiMefi/P8106_Final/blob/main/P8106_Final_Report.pdf}}
\vspace{2pt}
\resumeSubItem{DeepL - Improving Estimate of Prior in Variational Nonparametric Empirical Bayes (Work in Progress)}{Use CNN model to improve variational autoencoder training with self-defined loss functions. Tech: Python (Nov. '21)}
\vspace{2pt}
\resumeSubItem{Web Development, Database, Machine Learning - Clinical Registration Suggestion System (Work in Progress)}{Search engine for patient to search their symptoms and choose the registration type. Tech: Flask, SQL, Python (September '22)}
\vspace{2pt}
\resumeItem{Data Analysis and Visualization - Investigate the Influence of COVID-19 Pandemic on Personal Expenditure in the U.S.}{EDA and regression analysis on impact of COVID-19 U.S. cases on personal income and expenditure. Project Website: \url{http://sz3029.github.io/final_project/}}
\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://pubmed.ncbi.nlm.nih.gov/35491906/}{Differential Translation Elongation in Yeast Cells}}{Co-authored, published by RNA Biology, Volume 19, Issue 1. Tech: Bash, Python, IGV (November '21)}
\vspace{2pt}
\resumeSubItem{Interpretable machine learning models improve clinical understanding of factors with the greatest impact on perioperative mortality risk}{Work in Progress, to be published by International Anesthesia Research Society in late 2022. Tech: TensorFlow, Python, R (Oct. '21)}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Awards and Certificates}
\begin{description}[font=$\bullet$]
\item {Awarded Second Prize in Clinical Research at Department of Anesthesiology, CUIMC - May, 2022}
\vspace{-5pt}
\item {SAS 9.4 Base Programming Certified - Jan, 2022}
\vspace{-5pt}
\item {College Honor and Provost Honor at UCSD - 2017 - 2021}

\end{description}

\vspace{-5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Mentor at UCSD Bioinformatics Club}{San Diego, CA}
    {Mentoring new undergrad Bioinformatics students}{Jan 2018 - Jan 2021}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Maps building for disaster responses}{Remote}
    {Teams organization, completing assigned projects from the MissingMap project website.}{Jan 2021}

\resumeSubHeadingListEnd

\end{document}